---
title: "R Notebook"
output: word_document
---

## csect: proj-baseline

    on-entry: open _scratchpad (.tactcal)
    ensure that required packages are installed
    
    per-machine .baseline (_future, use package manager)

```{r proj-baseline-info-sect}
source('./y2013.proj-baseline.d/_info.R')

```

## csect: proj-blippex



## csect: proj-rogera

    insert data into rethinkdb (curr: s0)
    fetch facebook profile data (needs: fresh token; externalize tok)

## csect: proj-benchmark (revisited)



---
## attic
Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Press *Ctrl+Alt+R* to run all.

```{r do-plot-cars}
plot(cars)
```

```{r named-chunk}
x1=c(c(1,2),c(1,3),c(2,3))
plot(x1)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
